Greenhouse gas emissions model

### 2021-09-01 210617_GHG_model.Rmd

---
title: "Greenhouse gas emissions model"
author: "Cory and Eike"
bibliography:
 - references/packages.bib
 - references/papers.bib
output: html_document
---

@@

#Automatically write R package citation entries to a .bib file
knitr::write_bib(c(.packages(), 
                   'DiagrammeR',
                   'decisionSupport',
                   'MASS'), 'references/packages.bib')
```

@@

We apply a post-hoc analysis to the `mcSimulation()` outputs with `plsr.mcSimulation()` to determine the Variable Importance in the Projection (VIP) score and coefficients of a Projection to Latent Structures (PLS) regression model. This function uses the outputs of the `mcSimulation()` selecting all the input variables from the decision analysis function in the parameter `object` and then runs a PLS regression with an outcome variable defined in the parameter `resultName`. We use the code `names(GHG_simulation$y)[7]` to select the outcome variable `r names(GHG_simulation$y)[7]`, which is an element of the list `y` in our `GHG_simulation` outputs (this must be a character element).

@@

Here we import the input table again to replace the labels for the variables on the y-axis. The input table can include a 'label' and 'variable' column. The standard labels (from the 'variable' column) are usually computer readable and not very nice for a plot. The `plot_pls()` function uses the text in the 'label' column as replacement for the default text in the 'variable' column.

@@

In the following sections we apply a collection of functions for use in assessing uncertainty from the `uncertainty` package. Install using `devtools::install_github("CWWhitney/uncertainty")`.

Here we use the `varscatter()` function to create a scatter plot of an influence variable of interest `in_var` (x) and an outcome variable `out_var` (y) with associated and estimated densities with loess smooth linear fits density curves. Plot made with the scatter.hist() function in the plyr() package [@R-plyr] in R [@R-base].

@@

```{r uncertainty_package}
uncertainty::varscatter(in_var = GHG_simulation$y$milk_yield,
                        out_var = GHG_simulation$y$on_farm)
```

@@

```{r varviolin, fig.width=17, fig.height=7}
uncertainty::varviolin(in_var = in_var, out_var = out_var)
```

@@

`varkernelslicerange()` shows the influencing variable `in_var` value intervals, optimized interquartile ranges shown in `varviolin()` can be used to select a range to slice from the density kernel `varkernel()` as was done for a single variable value in `varkernelslice()`. Here we set the maximum expected value for `in_var` to `r (min(in_var)+(max(in_var)-min(in_var))/4*3)` and the minimum expected value to `r (min(in_var)+(max(in_var)-min(in_var))/4)`.

```{r varkernelslicerange}
uncertainty::varkernelslicerange(in_var = in_var, out_var = out_var, 
                                 min_in_var = round(min(in_var)+(max(in_var)-min(in_var))/4),
                                 max_in_var = round(min(in_var)+(max(in_var)-min(in_var))/4*3))
```

>>>>

---
title: "Greenhouse gas emissions model"
author: "Cory Whitney and Eike Luedeling"
bibliography:
 - references/packages.bib
 - references/papers.bib
output: html_document
---

@@

#Automatically write R package citation entries to a .bib file
knitr::write_bib(c(.packages(), 
                   'DiagrammeR',
                   'decisionSupport',
                   'MASS'), 'references/packages.bib')
#resolves an issue with the scientific style of numbers,answer from @Paul Hiemstra: https://stackoverflow.com/a/25947542/4061993 
#from the documentation of ?options:
options(scipen=999)
```

@@

Below we apply a post-hoc analysis to the `mcSimulation()` outputs with the `plsr.mcSimulation()` function in the `decisoonSupport` package. We use the function to determine the Variable Importance in the Projection (VIP) score and coefficients of a Projection to Latent Structures (PLS) regression model. This function uses the outputs of the `mcSimulation()` selecting all the input variables from the `GHG_simulation` decision analysis function in the parameter `object` and then runs a PLS regression with an outcome variable defined in the parameter `resultName`. We use the code `names(GHG_simulation$y)[7]` to select the outcome variable `r names(GHG_simulation$y)[7]`, which is an element of the list `y` in our `GHG_simulation` outputs.

@@

Here we import the input table again (the same table we used for the Monte Carlo model) to replace the labels for the variables on the y-axis. The input table can include a 'label' and 'variable' column. The standard labels (from the 'variable' column) are usually computer readable and not very nice for a plot. The `plot_pls()` function uses the text in the 'label' column as replacement for the default text in the 'variable' column.

@@

In the following sections we apply a collection of functions for use in assessing uncertainty from the `uncertainty` package. Install using `devtools::install_github("CWWhitney/uncertainty")`. We apply the following uncertainty function on the `milk_yield` and `on_farm` variables from the `r nrow(GHG_simulation$y)` of `GHG_simulation` model results.

Here we use the `varscatter()` function to create a scatter plot of an influence variable of interest `in_var` (x) and an outcome variable `out_var` (y) with associated and estimated densities with loess smooth linear fits density curves. Plot made with the scatter.hist() function in the `plyr()` package [@R-plyr] in R [@R-base].

@@

```{r uncertainty_package}
uncertainty::varscatter(in_var = in_var,
                        out_var = out_var)
```

@@

```{r varviolin, fig.width=17, fig.height=7}
uncertainty::varviolin(in_var = in_var, out_var = out_var, legend.position = "left")
```

@@

`varkernelslicerange()` shows the influencing variable `in_var` value intervals, optimized interquartile ranges shown in `varviolin()` can be used to select a range to slice from the density kernel `varkernel()` as was done for a single variable value in `varkernelslice()`. Here we set the maximum expected value for `in_var` to `r round(max(in_var), digits = 0)` and the minimum expected value to `r round(min(in_var), digits = 0)`.

```{r varkernelslicerange}
uncertainty::varkernelslicerange(in_var = in_var, out_var = out_var, 
                                 min_in_var = min(in_var),
                                 max_in_var = max(in_var))
```
